manual-geostat-TMB

### 2019-01-22 analysis/manual-geostat-TMB.Rmd
Move 'manual-geostas-TMB.Rmd'

d <- gfplot::get_survey_sets("pacific cod", ssid = 1)
 # d <- dplyr::filter(d, !(year == 2014 & survey_abbrev == "SYN WCHG")) # something went wrong in 2014

#### Tidy data and fill in missing depth values
```{r}

col <- if (grepl("SYN", survey)) "density_kgpm2" else "density_ppkm2" # grep says if SYN is in survey returns logical (l), use kgpm2

@@

#### Make prediction grid for plotting
```{r}
#  if (grepl("SYN", survey)) {
    grid_locs <- gfplot:::make_prediction_grid(
      dplyr::filter(dat, year == max(dat$year)), survey = survey,
      cell_width = 2)$grid # cell width of 2 km
    grid_locs <- dplyr::rename(grid_locs, depth = akima_depth)
#  } else {
#    grid_locs <- if (surv == "HBLL OUT N") gfplot::hbll_n_grid$grid else gfplot::hbll_s_grid$grid
 # }
  grid_locs$year <- NULL

#  formula <- if (include_depth) {
#    stats::as.formula(density ~ 0 + as.factor(year))
#  } else {
#    stats::as.formula(density ~ 0 + as.factor(year) + depth_scaled + depth_scaled2)
# }
```

#### Spatial model
```{r}
  spde <- sdmTMB::make_spde(dat$X, dat$Y, n_knots = 100)

@@

#### Save preditions from model
```{r}
predictions <- predict(m, newdata = grid_locs)$data
glimpse(predictions) # est = predicted values

>>>>

d <- gfplot::get_survey_sets("pacific cod", ssid = 1)
# d <- dplyr::filter(d, !(year == 2014 & survey_abbrev == "SYN WCHG")) # something went wrong in 2014
```

#### Tidy data and fill in missing depth values
```{r}
col <- if (grepl("SYN", survey)) "density_kgpm2" else "density_ppkm2" # grep says if SYN is in survey returns logical (l), use kgpm2

@@

#### Make prediction grid for plotting
```{r}
grid_locs <- gfplot:::make_prediction_grid(
  dplyr::filter(dat, year == max(dat$year)), survey = survey,
  cell_width = 2)$grid # cell width of 2 km
grid_locs <- dplyr::rename(grid_locs, depth = akima_depth)
grid_locs$year <- NULL
```

#### Spatial model
```{r}
spde <- sdmTMB::make_spde(dat$X, dat$Y, n_knots = 50)

@@

#### Save predictions from model
```{r}
predictions <- predict(m, newdata = grid_locs)$data
glimpse(predictions) # est = predicted values
